The regularity of ODEs and thimble integrals \\ with respect to Borel summation

### 2024-03-18 exp-resurgence.tex
Adapt the ODE results in the intro to our new reasoning
Clean up old reasoning too.

Furthermore, when $-\alpha$ is a root of $P$, the integral equation $\hat{\mathcal{P}}_\alpha \phi = 0$ has a special solution $\psi_\alpha$ which is distinguished, up to scaling, by its power-law asymptotics at $\zeta = \alpha$. Because this solution is so unique, its Laplace transform $\Psi_\alpha$ turns out to be Borel regular.

%%The Laplace transform commutes this distinguishing behavior into asymptotics at $z = \infty$, which can be recognized even if we turn $\Phi$ into a formal series $

%We can use the Laplace transform to convert $\mathcal{P}$ into a family of integral operators $\hat{\mathcal{P}}_\upsilon$ parameterized by the point $\zeta = \upsilon$ on the position domain.

@@

\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\ref{sec:reg-decay}.

@@

\begin{theorem}\label{thm:has_ae_ODE}
The solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} has an asymptotic expansion in the transmonomial space $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$. In fact, up to scaling, it is asymptotic to the Poincar\'{e} solution found in that space \textcolor{orange}{[not defined yet?]}.

@@

Combining our uniqueness and regularity results for $\psi_\alpha$ with uniqueness and regularity results for the Poincar\'{e} solutions, we can show that $\Psi_\alpha$ is Borel regular.

@@

\color{Maroon}
\begin{theorem}\label{thm:borel_reg_ODE}
Choose a root $-\alpha$ of $P$. Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$. Equation $\mathcal{P}\Psi=0$ has a unique solution $\Psi_\alpha$ in the affine subspace
\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\ref{sec:reg-decay}. That solution is Borel regular.
\textcolor{violet}{If you prefer to work in the analytic world, you can use this result to prove the existence and Borel summability of special formal transmonomial solutions.}
\begin{corollary}\label{cor:borel_reg_ODE}
For each root $-\alpha$ of $P$, equation $\mathcal{P}\Psi=0$ has a formal solution in the transmonomial space $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$, which is unique up to scaling. That solution is Borel summable, and its Borel sum is a constant multiple of $\Psi_\alpha$.
\textcolor{violet}{On the other hand, if you prefer to work in the formal world, you can use Theorem~\ref{thm:borel_reg_ODE} to show that the Poincar\'{e} solutions are Borel summable. See Section~\ref{sec:new-summability-proof}.}
\textcolor{violet}{[In another section, do the ``mirror image'' argument. Use the Poincar\'{e} algorithm to construct a formal transmonomial solution in the classical way. Use the Ramis Index Theorem to show that it is Gevrey-$1$, and then then use our existence and uniqueness result for regular singular Volterra equations to show that it is not only Gevrey-$1$, but in fact Borel summable.]}

@@

\section{Proof of main results}\label{sec:proof_main_results}
\subsection{Borel regularity for ODEs}\label{borel_reg-ODE}
\textcolor{orange}{[Explain the contents of the section]}
\subsubsection{Regularity results}
Let us recall the setting from Section~\ref{borel-reg:explanatory-power}. Let $\mathcal{P}$ be a linear differential operator of the form
%%\footnote{We follow Delabaere, rather than \'{E}calle, in only going on up to degree $d-1$; see \cite[Footnote~1 in Section 5.2.2.1]{diverg-resurg-iii}}
\begin{equation}\label{eqn:operator-P}
    \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2} R(z^{-1}),
\end{equation}
where
\begin{enumerate}
\item $P$ is a monic degree-$d$ polynomial whose roots are all simple; 
\item $Q$ is a degree-$(d-1)$ polynomial that's non-zero at every root of $P$;
\item $R(z^{-1})$ is holomorphic in some disk $|z| > A$ around $z = \infty$. In particular, the power series
\[ R(z^{-1}) = \sum_{j=0}^\infty R_j z^{-j} \]
converges in the region $|z| > A$.
\end{enumerate}
%%For each root $-\alpha$ of $P$, choose an open sector $\Omega_\alpha \subset \C$ that has $\zeta = \alpha$ at its tip, doesn't touch any other root of $P(-\zeta)$, and has an opening angle of $\pi$ or less.
\textcolor{orange}{[Discuss terminology, like in \tt{reg-sing-volterra}?]}
%%%\begin{itemize}
%%%\item The set $\Omega_\alpha$ is star-shaped around $\zeta = \alpha$. In other words, for any $a \in \Omega_\alpha$, a straight path from $\zeta = \alpha$ to $a$ stays in $\Omega_\alpha$. Since $\Omega_\alpha$ doesn't contain $\zeta = \alpha$, we will always leave that starting point out of the path.
%%%\item The set $\Omega_\alpha$ does not contain the tubular neighborhood of the other critical points, as shown in Figure \ref{Fig:domain}. \textcolor{orange}{[In ``Regular singular Volterra,'' we assume that $\Omega_\alpha$ doesn't touch any other critical point (that is, doesn't contain any other critical point in its closure). Under the star-shaped assumption, I think that implies avoiding tubular neighborhoods of the shadow rays.]}
%%%\end{itemize}
\color{BlueViolet}
\begin{theorem}[restatement of \ref{thm:exist_uniq_ODE}]\label{thm:exist_uniq_ODE_proof}
Choose a root $-\alpha$ of $P$ with $\tau_\alpha \in (0, \infty)$. Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$. The equation $\mathcal{P}\Psi = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\ref{sec:reg-decay}.
\end{theorem}
\begin{proof}
After rescaling by a constant, Theorem~4 of \cite{reg-sing-volterra} tells us that the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
\[ \frac{\zeta^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Omega_\alpha) \]
of the space $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$. The same is true on any smaller sector created by shaving a sector off each edge of $\Omega_\alpha$. It follows, by the results of Section~\ref{sec:reg-decay} \textcolor{magenta}{[the domain $\Omega_\alpha$ needs to be a sector for this]}, that the equation $\mathcal{P}\Psi_\alpha = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$.
\end{proof}
\color{RoyalBlue}
\textcolor{orange}{[\ldots]} Our arguments in \cite{reg-sing-volterra} took place on $\C$, but they work just as well on a covering of $\C$ which is branched at the roots of $P(-\zeta)$. Let us use the covering $\pi \maps \widetilde{B}_{P(-\zeta)} \to \C$ built by puncturing $\C$ at the roots of $P(-\zeta)$, taking the universal cover, and then gluing the roots back in as infinite-order branch points.

@@

%%\[ \varepsilon_n = a_n \zeta^{\rho+n} + a_1 \zeta^{\rho+n+1} + a_2 \zeta^{\rho+n+2} + a_{n+3} \zeta^{\rho+n+3} + \ldots \]
\end{proof}
We're now ready to show that the solution $\Psi_\alpha$ is Borel regular.
\begin{theorem}[restatement of \ref{thm:borel_reg_ODE}]\label{thm:borel_reg_ODE_proof}
The solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE_proof} is asymptotic to a transmonomial $\series{\Psi}_\alpha \in e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$, and the Borel sum of $\series{\Psi}_\alpha$ is $\Psi_\alpha$.
\end{theorem}
\begin{proof}
Take an open sector $\Omega_\alpha$ of the kind used in Theorem~\ref{thm:exist_uniq_ODE_proof}, and expand it to an open set $\Upsilon \subset \widetilde{\C^\times}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed}. By Theorem~4 of \cite{reg-sing-volterra}, the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace \textcolor{orange}{[use $\zeta_\alpha$ in place of $\zeta$ throughout proof]}
\[ \frac{\zeta^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Upsilon) \]
of the space $\singexpalg{\tau_\alpha-1}(\Upsilon)$. Restricting this solution to $\Omega_\alpha$ gives the analogous solution from the proof of Theorem~\ref{thm:exist_uniq_ODE_proof}, as we can see from the uniqueness part of Theorem~4. To prove that $\Psi_\alpha$ has a the desired asymptotic expansion, we will show that $\psi_\alpha$ lies in $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$.

%%The key step of our proof will be to show that $\psi_\alpha$ lies in

%%The uniqueness part of the Theorem~4 ensures that restricting $\psi_\alpha$ to $\Omega_\alpha$ gives the analogous solution used in the proof of Theorem~\ref{thm:exist_uniq_ODE_proof}.

%%%In the proof of Theorem~\ref{thm:exist_uniq_ODE_proof}, we used Theorem~4 of \cite{reg-sing-volterra} to show that the equation $\mathcal

%%%$\psi_\alpha$ in the affine subspace
%%\[ \frac{\zeta^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Omega_\alpha) \]
%%of the space $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$

@@

Now, let's take the Borel sum of $\series{\Psi}_\alpha$. The Borel transform inverts the formal Laplace transform, bringing us back to $\series{\psi}_\alpha$. By definition, the sum of $\series{\psi}_\alpha$ is $\psi_\alpha$, and the Laplace transform $\laplace^\theta_{\zeta, \alpha} \psi_\alpha$ is $\Psi_\alpha$.
%%%\color{Maroon}
%%%\begin{theorem}[restatement of \ref{thm:borel_reg_ODE}]\label{thm:borel_reg_ODE_proof}
%%%Choose a root $-\alpha$ of $P$. Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$. Equation 
%%%\begin{equation}\label{eqn:standard ODE}
%%%\mathcal{P}\Psi=0
%%%\end{equation}
%%%has a unique solution $\Psi_\alpha$ in the affine subspace
%%%\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
%%%of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\ref{sec:reg-decay}.
%%%\end{theorem}
%%%\begin{proof}
%Let $\hat{\mathcal{P}}_\alpha$ be the Volterra operator defined in Section~4.5 of \cite{reg-sing-volterra}. Take any holomorphic function $\phi$ on $\Omega_\alpha$ with a well-defined Laplace transform $\Phi = \laplace_{\zeta,\alpha}^{\theta} \phi$ \textcolor{magenta}{[choose $\theta$]}. Lemma~2 of \cite{reg-sing-volterra} shows that $\hat{\mathcal{P}}_\alpha \phi = 0$ if and only if $\mathcal{P}\Phi = 0$ \textcolor{magenta}{[the lemma only states one direction; change it before publication to state both directions]}.
%%%As a consequence of Theorem~4 \cite{reg-sing-volterra}, after rescaling by a constant, the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
%%%\[ \frac{\zeta^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Omega_\alpha) \]
%%%of the space $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$. The same is true on any smaller sector created by shaving a sector off each edge of $\Omega_\alpha$. It follows, by the results of Section~\ref{sec:reg-decay} \textcolor{magenta}{[the domain $\Omega_\alpha$ needs to be a sector for this]}, that the equation $\mathcal{P}\Psi_\alpha = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
%%%\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
%%%of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$.
%%%\end{proof}
\textcolor{Turquoise}{Assuming $\Psi_\alpha$ from Theorem~\ref{thm:borel_reg_ODE_proof} admits an asymptotic expansion as $\Re z\to e^{i\theta}\infty$ along some rays contained in the sector $\Omega_\alpha$, then $\Psi_\alpha$ is Borel regular.} That solution $\Psi_\alpha$ from Theorem~\ref{thm:borel_reg_ODE_proof} is Borel regular.
\color{Turquoise}
If $\Psi_\alpha$ admits an asymptotic expansion $\tilde{\Psi}_\alpha$, then $\Psi_\alpha$ is a formal solution of Equation~\eqref{eqn:operator-P}, thus by Ramis Index Theorem is $1$-Gevrey. The Borel transform of $\tilde{\Psi}_\alpha$ is a germ of convergent power series, and by the properties of the Borel transform, it is a formal solution of $\hat{\mathcal{P}}_\alpha \phi=0$. \textcolor{red}{[check the exponential term $e^{-z\alpha}$, otherwise get different points]}
\color{Violet}
        \item the asymptotitics of $\Psi_\alpha$ \textcolor{LimeGreen}{[exist and]} are $1$-Gevrey
        \item \textcolor{LimeGreen}{The solution $\Psi_\alpha$ has an asymptotic expansion} indeed it is the Laplace transform of $\psi_\alpha$, thus if we consider the Taylor expansion of $\psi_\alpha$ at $\zeta=\alpha$ and then we integrate term by term we can compute the asymptotic. Notice that Poincar\'e asymptotic doesn't have to be to a power series, but it can be mor generally to a trans-monomial. I think we should state the definition for trans-monomials.
        \begin{align}
            \Psi_\alpha&=\int_\alpha^\infty e^{-z\zeta} \sum_{n=0}^\infty a_n (\zeta-\eta)^n d\zeta \\
            & = \sum_{n=0}^N a_n \int_\alpha^\infty e^{-z\zeta}   (\zeta-\eta)^n d\zeta+\int_\alpha^\infty e^{-z\zeta} \sum_{n=N+1}^\infty a_n (\zeta-\eta)^n d\zeta \\
            & = e^{-z\eta} \sum_{n=0}^N a_n \int_\alpha^\infty e^{-z(\zeta - \eta)} (\zeta-\eta)^n d\zeta + e^{-z\eta} \int_\alpha^\infty e^{-z(\zeta - \eta)} \sum_{n=N+1}^\infty a_n (\zeta-\eta)^n d\zeta
        \end{align}
        \begin{multline*}
            \left|\Psi_\alpha- e^{-z\eta} \sum_{n=0}^N a_n \int_\alpha^\infty e^{-z(\zeta - \eta)} (\zeta-\eta)^n d\zeta\right|\leq e^{-\Re(z)|\eta|} \int_\alpha^R |e^{-z(\zeta - \eta)} |\sum_{n=N+1}^\infty R^{-n} |(\zeta-\eta)|^n d\zeta +\\
            e^{-\Re(z)|\eta|} \int_R^\infty |e^{-z(\zeta - \eta)} | |\psi_\alpha| d\zeta \qquad\text{[use that $\psi_\alpha$ is exponentially bounded]}
        \end{multline*}
       \[\Psi_\alpha=\lim_{b \to (\zeta = \alpha)}\int_b^\infty e^{-z\zeta} f\;d\zeta \]
       \item Say $\left|\Psi_\alpha - \int_b^{\infty}\right| \leq \epsilon$ over all $z$. Then $|z|^n\;\left|\Psi_\alpha - \int_b^{\infty}\right| \leq |z|^n \epsilon$
       \item \begin{align*}
       \int_\alpha^\infty e^{-z\zeta} |z|^n |\psi_\alpha-\text{poly}(\zeta)| d\zeta \\
       \int_\alpha^\infty \left[\left(\tfrac{\partial}{\partial \zeta}\right)^n e^{-z\zeta}\right] |\psi_\alpha-\text{poly}(\zeta)| d\zeta
       \item Need $\lim_{z \to \infty} z^n |\Psi_\alpha - \text{poly}|$ for all $n \in \Z_{\ge 0}$
        \item $\tilde{\psi}_\alpha\in\zeta_\alpha^{\tau_\alpha}\C\lbrace\zeta_\alpha\rbrace$ and solves $\hat{\mathcal{P}}_\alpha\phi=0$
        \item Integral looks like
        \int_0^\infty e^{-z\zeta} f\;d\zeta & = \int_0^r e^{-z\zeta} f\;d\zeta + \int_r^\infty e^{-z\zeta} f\;d\zeta \\
        & \text{``}\approx\text{''} \int_0^r e^{-z\zeta} f\;d\zeta + e^{-z \Re(\zeta)} \|f\|_1 \\
        & \text{``}\approx\text{''} \|f\|_1 + e^{-zr} \|f\|_1
        \item $\hat{\mathcal{P}}_\alpha\phi=0$ admits a unique formal solution
        \item  $\tilde{\psi}_\alpha$ is proportional to the Taylor expansion of $\psi_\alpha$ \textcolor{LimeGreen}{[which exists]}
\color{Maroon}
\begin{figure}[h]
  (0, 0) -- (41:\spill) arc (41:-48:\spill) -- cycle;
\fill[violet] circle (0.7mm) node[anchor=-15, outer sep=1mm] {$\zeta = \alpha$};
\caption{The domain $\Omega_\alpha$}\label{Fig:domain}

>>>>

Furthermore, when $-\alpha$ is a root of $P$, the integral equation $\hat{\mathcal{P}}_\alpha \phi = 0$ has a special solution $\psi_\alpha$ which is distinguished, up to scaling, by its power-law asymptotics at $\zeta = \alpha$. This solution is regular enough to have a well-defined Laplace transform $\Psi_\alpha$, which is a special solution of $\mathcal{P}\Phi = 0$ distinguished by its own characteristic asymptotics.

@@

\[ e^{-\alpha z} \left[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \right] \]
of the space $e^{-\alpha z} \dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\ref{sec:reg-decay}.

@@

The special solution $\psi_\alpha$ is also regular enough to have a ``fractionally shifted'' power series expansion $\series{\psi}_\alpha$, whose formal Laplace transform $\series{\Psi}_\alpha$ is a formal solution of $\mathcal{P}\series{\Phi} = 0$. By construction, $\series{\Psi}_\alpha$ is Borel summable, with Borel sum $\Psi_\alpha$.
\begin{theorem}\label{thm:is_Borel_sum}
The analytic solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is the Borel sum of a formal trans-monomial solution $\series{\Psi}_\alpha \in e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$ of the equation $\mathcal{P}\series{\Phi} = 0$.

@@

With a little more work, encapsulated in Lemma~\textcolor{orange}{?} from Section~\textcolor{orange}{?}, we can use this result to show that $\Psi_\alpha$ is Borel regular.
The analytic solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is asymptotic to the formal solution $\series{\Psi}_\alpha$ from Theorem~\ref{thm:is_Borel_sum}.

@@

%%\color{Maroon}
%%\begin{theorem}\label{thm:borel_reg_ODE}
%%Choose a root $-\alpha$ of $P$. Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$. Equation $\mathcal{P}\Psi=0$ has a unique solution $\Psi_\alpha$ in the affine subspace
%%\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
%%of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\ref{sec:reg-decay}. That solution is Borel regular.
%%\textcolor{violet}{If you prefer to work in the analytic world, you can use this result to prove the existence and Borel summability of special formal transmonomial solutions.}
%%\begin{corollary}\label{cor:borel_reg_ODE}
%%For each root $-\alpha$ of $P$, equation $\mathcal{P}\Psi=0$ has a formal solution in the transmonomial space $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$, which is unique up to scaling. That solution is Borel summable, and its Borel sum is a constant multiple of $\Psi_\alpha$.
\textcolor{BlueViolet}{From an analytic perspective, Theorem~\ref{thm:is_Borel_sum} justifies the ansatz that Poincar\'{e} used to solve the equation $\mathcal{P}\series{\Phi} = 0$. On the other hand, if you prefer to work formally, you can take the Poincar\'{e} solutions as given and use Theorem~\ref{thm:exist_uniq_ODE} to establish their Borel summability. We do this in Section~\ref{sec:new-summability-proof}.}
%%\textcolor{violet}{On the other hand, if you prefer to work in the formal world, you can use Theorem~\ref{thm:borel_reg_ODE} to show that the Poincar\'{e} solutions are Borel summable. See Section~\ref{sec:new-summability-proof}.}
%%\textcolor{violet}{[In another section, do the ``mirror image'' argument. Use the Poincar\'{e} algorithm to construct a formal transmonomial solution in the classical way. Use the Ramis Index Theorem to show that it is Gevrey-$1$, and then then use our existence and uniqueness result for regular singular Volterra equations to show that it is not only Gevrey-$1$, but in fact Borel summable.]}

@@

\section{Proof of main results}\label{sec:proof_main_results}
\subsection{Borel regularity for ODEs}\label{borel_reg-ODE}
\textcolor{orange}{[Explain the contents of the section]}
\subsubsection{Regularity results}
Let us recall the setting from Section~\ref{borel-reg:explanatory-power}. Let $\mathcal{P}$ be a linear differential operator of the form
%%\footnote{We follow Delabaere, rather than \'{E}calle, in only going on up to degree $d-1$; see \cite[Footnote~1 in Section 5.2.2.1]{diverg-resurg-iii}}
\begin{equation}\label{eqn:operator-P}
    \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2} R(z^{-1}),
\end{equation}
where
\begin{enumerate}
\item $P$ is a monic degree-$d$ polynomial whose roots are all simple; 
\item $Q$ is a degree-$(d-1)$ polynomial that's non-zero at every root of $P$;
\item $R(z^{-1})$ is holomorphic in some disk $|z| > A$ around $z = \infty$. In particular, the power series
\[ R(z^{-1}) = \sum_{j=0}^\infty R_j z^{-j} \]
converges in the region $|z| > A$.
\end{enumerate}
%%For each root $-\alpha$ of $P$, choose an open sector $\Omega_\alpha \subset \C$ that has $\zeta = \alpha$ at its tip, doesn't touch any other root of $P(-\zeta)$, and has an opening angle of $\pi$ or less.
\textcolor{orange}{[Discuss terminology, like in \tt{reg-sing-volterra}?]}
%%%\begin{itemize}
%%%\item The set $\Omega_\alpha$ is star-shaped around $\zeta = \alpha$. In other words, for any $a \in \Omega_\alpha$, a straight path from $\zeta = \alpha$ to $a$ stays in $\Omega_\alpha$. Since $\Omega_\alpha$ doesn't contain $\zeta = \alpha$, we will always leave that starting point out of the path.
%%%\item The set $\Omega_\alpha$ does not contain the tubular neighborhood of the other critical points, as shown in Figure \ref{Fig:domain}. \textcolor{orange}{[In ``Regular singular Volterra,'' we assume that $\Omega_\alpha$ doesn't touch any other critical point (that is, doesn't contain any other critical point in its closure). Under the star-shaped assumption, I think that implies avoiding tubular neighborhoods of the shadow rays.]}
%%%\end{itemize}
\color{BlueViolet}
\begin{theorem}[restatement of \ref{thm:exist_uniq_ODE}]\label{thm:exist_uniq_ODE_proof}
Choose a root $-\alpha$ of $P$ with $\tau_\alpha \in (0, \infty)$. Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$. The equation $\mathcal{P}\Psi = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\ref{sec:reg-decay}.
\end{theorem}
\begin{center}
\begin{tikzpicture}
\newcommand{\spill}{4}
\fill[violet!20, bezier bounding box, path fading=radial edge]
  (-\spill, -\spill) (\spill, \spill)
  (0, 0) -- (41:\spill) arc (41:-48:\spill) -- cycle;
\fill[violet] circle (0.7mm) node[anchor=-15, outer sep=1mm] {$\zeta = \alpha$};
\foreach \p in {(107.5:1.95), (46.5:2.46), (-56:2.24)} {
  \fill \p circle (0.7mm);
}
\end{tikzpicture}

{\small The domain $\Omega_\alpha$}
\end{center}
\begin{proof}
After rescaling by a constant, Theorem~4 of \cite{reg-sing-volterra} tells us that the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
\[ \frac{\zeta^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Omega_\alpha) \]
of the space $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$. The same is true on any smaller sector created by shaving a sector off each edge of $\Omega_\alpha$. It follows, by the results of Section~\ref{sec:reg-decay} \textcolor{magenta}{[the domain $\Omega_\alpha$ needs to be a sector for this]}, that the equation $\mathcal{P}\Psi_\alpha = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$.
\end{proof}
\color{RoyalBlue}
\textcolor{orange}{[\ldots]} Our arguments in \cite{reg-sing-volterra} took place on $\C$, but they work just as well on a covering of $\C$ which is branched at the roots of $P(-\zeta)$. Let us use the covering $\pi \maps \widetilde{B}_{P(-\zeta)} \to \C$ built by puncturing $\C$ at the roots of $P(-\zeta)$, taking the universal cover, and then gluing the roots back in as infinite-order branch points.

@@

%%\[ \varepsilon_n = a_n \zeta^{\rho+n} + a_1 \zeta^{\rho+n+1} + a_2 \zeta^{\rho+n+2} + a_{n+3} \zeta^{\rho+n+3} + \ldots \]
\end{proof}
We're now ready to show that the solution $\Psi_\alpha$ is Borel regular.
\begin{theorem}[restatement of \ref{thm:borel_reg_ODE}]\label{thm:borel_reg_ODE_proof}
The solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE_proof} is asymptotic to a transmonomial $\series{\Psi}_\alpha \in e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$. The series $\series{\Psi}_\alpha$ is Borel summable, and its Borel sum is $\Psi_\alpha$.
\end{theorem}
\begin{proof}
Take an open sector $\Omega_\alpha$ of the kind used in Theorem~\ref{thm:exist_uniq_ODE_proof}, and expand it to an open set $\Upsilon \subset \widetilde{\C^\times}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed}. By Theorem~4 of \cite{reg-sing-volterra}, the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace \textcolor{orange}{[use $\zeta_\alpha$ in place of $\zeta$ throughout proof]}
\[ \frac{\zeta^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Upsilon) \]
of the space $\singexpalg{\tau_\alpha-1}(\Upsilon)$. Restricting this solution to $\Omega_\alpha$ gives the analogous solution from the proof of Theorem~\ref{thm:exist_uniq_ODE_proof}, as we can see from the uniqueness part of Theorem~4. To prove that $\Psi_\alpha$ has a the desired asymptotic expansion, we will show that $\psi_\alpha$ lies in $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$.

@@

Now, let's take the Borel sum of $\series{\Psi}_\alpha$. The Borel transform inverts the formal Laplace transform, bringing us back to $\series{\psi}_\alpha$. By definition, the sum of $\series{\psi}_\alpha$ is $\psi_\alpha$, and the Laplace transform $\laplace^\theta_{\zeta, \alpha} \psi_\alpha$ is $\Psi_\alpha$.
\end{proof}
\color{black}
\subsubsection{A new proof of the Borel summability of the Poincar\'{e} solutions}\label{sec:new-summability-proof}
%\textcolor{orange}{[Mention that this is a component of the earlier Borel regularity proof.]}
Given a differential operator $\mathcal{P}$ as in Equation~\eqref{eqn:operator-P}, Poincar\'e showed how to build a frame of formal solutions of the equation $\mathcal{P}\Psi=0$ with a simple algorithm: for every root $\alpha$ of $P$, let $\tau_\alpha:=Q(-\alpha)/P'(-\alpha)$ and consider the following ansatz
\begin{equation}
    \tilde{\Psi}_\alpha(z):=e^{-z\alpha}z^{-\tau_\alpha}\sum_{n=0}^\infty a_{\alpha,n}\, z^{-n}\in e^{-z\alpha} z^{-\tau_\alpha}\C\llbracket z^{-1}\rrbracket.
\end{equation}
Then solving order by order in $n$ it is possible to compute the coefficients of the formal series $\sum_{n=0}^\infty a_{\alpha,n}\, z^{-n}$, which will turn out to be a $1$-Gevrey series because of Ramis
Index Theorem \cite{ramis_index}. When applicable, Borel summability is an effective method to produce an analytic frame of solutions from the formal Poincar\'e frame $\tilde{\Psi}_\alpha$. In particular, as a consequence of our result in Theorem~\ref{thm:borel_reg_ODE_proof} we deduce that the Poincar\'e frame of solutions is Borel summable (proving Corollary~\ref{cor:borel_reg_ODE}).
\begin{theorem}\label{thm2-dim}
For each root $\alpha$ of $P$, let $\tilde{\Psi}_\alpha(z)\in e^{-z\alpha} z^{-\tau_\alpha}\C\llbracket z^{-1}\rrbracket_1$ be the formal solution of $\mathcal{P}\Psi=0$ with $a_{\alpha,0}=1$. Then $\series{\Psi}_\alpha(z)$ is Borel summable and its Borel sum $\hat{\Psi}_\alpha(z)$ is proportional to the analytic solution $\Psi_\alpha$ of Theorem~\ref{thm:borel_reg_ODE_proof}. 
\end{theorem}
\begin{proof}
We divide the proof in the following steps:
\begin{itemize}
\item[$(a)$] let $\series{\psi}_\alpha:=\borel_{\zeta}\series{\Psi}_\alpha$, then $\hat{\mathcal{P}}_\alpha\series{\psi}_\alpha=0$.
\item[$(b)$] $\tilde{\psi}_\alpha\in\C\lbrace\zeta_\alpha\rbrace$ can be analytically continued and its sum $\hat{\psi}_\alpha$ solves $\hat{\mathcal{P}}_\alpha\hat{\psi}_\alpha=0$. 
\item[$(c)$] $\hat{\psi}_\alpha$ admits a Laplace transform $\laplace_{\zeta,\alpha}^{\theta}\hat{\psi}_\alpha=:\hat{\Psi}_\alpha$ and that $\hat{\Psi}_\alpha\propto\Psi_\alpha $. 
\end{itemize}
Step $(a)$ follows from the properties of the Borel transform: recall from Section~\ref{sec:convolution-compatible} that $\tilde{\Psi}_\alpha$ is a transmonomial, thus the Borel transform of $z^{-\lambda}\tilde{\Psi}_\alpha$ is written in terms of the convolution product $\ast_{\alpha}$:   
\begin{align*}
  \borel_{\zeta}\left(\mathcal{P}\series{\Psi}_\alpha\right)&= \left[P(-\zeta)+1\ast_{\alpha} Q(-\zeta)+\zeta \ast_{\alpha} \left(\sum_{r=0}^{d-1}\borel_\zeta(R_r(z^{-1}))\ast_{\alpha}(-\zeta)^r\right)\right]\series{\psi}_\alpha(\zeta_\alpha)\\
  &=\left[P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\fracderiv{-2}{\zeta}{\alpha} \left(\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha} )(-\zeta)^r\right)\right]\series{\psi}_\alpha(\zeta_\alpha)\\
  &=\hat{\mathcal{P}}_\alpha\tilde{\psi}_\alpha(\zeta_\alpha)
\end{align*}
Hence, the Borel transform of $\series{\Psi}_\alpha$ is a solution of $\hat{\mathcal{P}}_\alpha\series{\psi}_\alpha$=0.
